Stability of virtual aggregations of prosumers through diversification

### 2015-07-30 Article.tex
red paragraphs modif

As explained in the section above, allowing entities using mainly renewables to inject power in the grid is a difficult challenge. Indeed, on the contrary to fossil plants whose production can be scheduled in advance to meet the expected consumption, renewables by definition only produce when the ressource is present. Unfortunately, these moments do not necessarily coincide with the consumption peak hours \cite{Milligan2010}. One possible solution consists in shifting some of the delayable loads through dynamic pricing. Coupled with demand side management techniques implemented on the end users' smart meters, this could result in less production spilled as well as smaller consumption peaks \cite{Milligan2010} \cite{Logenthiran2012}.

{\color{red} Schematically, in periods when the production is expected to be greater than the consumption, prices are scheduled low in order to encourage end users to delay their elastic loads to these periods. On the contrary, when the production is expected to be less than the consumption, high prices are scheduled to deter any delayable loads over these periods.
}

@@

\subsection{Cliques as de-correlated starting seeds}
{\color{red}
Correlation can be seen as cosine of angles in $ L^{2} $, hence even if there is no strict a transitivity relation for correlation, there is, to a certain extent, some partial notion of it. More precisely, if a, b, and c are three items such that $ \rho_{ab} > \delta $ and $ \rho_{bc} > \delta $, then we know, by the cosine addition formula\footnote{ $ cos(a+b) = cos(a)cos(b) - sin(a)sin(b) $ }, that $ \rho_{ac} > 2 \delta^{2} - 1 $. That is, if a and b are strongly correlated ($\rho_{ab} > 0.9 $) and b and c are also strongly correlated ($\rho_{bc} > 0.9 $), then there is a high probability for a and c of being strongly correlated ($\rho_{ac} > 0.62 $).}

>>>>

As explained in the section above, allowing entities using mainly renewables to inject power in the grid is a difficult challenge. Indeed, on the contrary to fossil plants whose production can be scheduled in advance to meet the expected consumption, renewables by definition only produce when the ressource is present. Unfortunately, these moments do not necessarily coincide with the consumption peak hours \cite{Milligan2010}. One possible solution consists in shifting some of the loads towards high productivity periods. Coupled with demand side management techniques implemented on the end users' smart meters, this could result in less production spilled as well as smaller consumption peaks \cite{Milligan2010} \cite{Logenthiran2012}. Since end users tend to seek a maximum utility at a minimum cost, dynamic pricing is believed to be a good way to give incentives to them. By carefully scheduling the prices, it is assumed that the load curve can be shaped to some extend.

@@

\subsection{Cliques}

In \cite{Garas2008} the structural roles of weak and strong links on financial correlation graphs is investigated. The author shows that strong links, accounting for strong correlation relationships, are responsible for the clustering, while weak links provide the connectivity between clusters. Indeed, if we consider three items, say a, b, and c such that a and b are strongly correlated and b and c are also strongly correlated, then it is likely that a and c are also strongly correlated. It can be easily shown using the cosine addition formula\footnote{ $ cos(a+b) = cos(a)cos(b) - sin(a)sin(b) $ }, that if $\rho_{ab} > x $ and $\rho_{bc} > x $ with $ x>0 $, then $\rho_{ac} > 2x^{2}-1$). Correlation graphs capture this weak transitivity notion through clusters of correlated series.
